\textbf{ Joystream: A Protocol for User Governed Content Platforms }

### 2019-02-25 paper.tex
Deduplicate wording

The platform has a set of terms, called the \textit{active paid membership terms}, which is the current paid membership terms currently in place for anyone seeking paid membership. It is updated through a council proposal. Any new terms introduced by the council must have an ID one greater than the prior active terms, and the initially active terms have an ID of $0$. The full history of all such terms that were at one time active is kept in a list, called the \textit{paid membership terms record}, which maps the term id to the corresponding terms.

>>>>

The platform has a set of terms, called the \textit{active paid membership terms}, which is the terms currently in place for anyone seeking paid membership. It is updated through a council proposal. Any new terms introduced by the council must have an ID one greater than the prior active terms, and the initially active terms have an ID of $0$. The full history of all such terms that were at one time active is kept in a list, called the \textit{paid membership terms record}, which maps the term id to the corresponding terms.
